\SW: Crowd-sourcing the Discovery of Gravitational Lenses

### 2015-03-30 doc/sw-system.tex
Starting to rejig table

\title[\sw]
{\SW: Crowd-sourcing the Discovery of Gravitational Lenses}

@@

We describe \sw, a novel gravitaional lens discovery service that
yields samples of high purity and completeness through crowd-sourced
visual inspection.
Carefully
produced color composite images are displayed to volunteers via a
classification interface which records their estimates of the positions of
candidate lensed features. Simulated lenses, and expert-classified non-lenses,
are inserted into the image stream at random intervals; this training set is
used to give the volunteers feedback on their performance, and to estimate a
dynamically-updated probability for any given image to contain a lens. Low
probability systems are retired from the site periodically, concentrating the
sample towards a set of candidates; this ``\StageOne'' set is then re-classified
by the volunteers in a second  refinement stage. Analyzing the classification
of the training set, we predict that the first stage alone should yield a
sample that is C\% complete, while leading to the rejection of R\% of the
initial target sample. Having divided the 150 square degree CFHTLS imaging
survey into 430000 overlapping 70 by 70 arcminute tiles and displayed them on
the site, we were joined by 33000 volunteers who contributed X million image
classifications over the course of N months. The sample was reduced to 3500
\StageOne candidates; these were then refined to yield a sample of 1400
candidates rankable by their \StageTwo probability. We expect this sample to be
X\% complete and Y\% pure at a threshold of 95\% classification probability.
We find that, on average, and given the assumptions we make in our analysis,
we need 9 classifications per image during the first stage, X in the second.
We estimate the mean information contributed per person to be X bits, over a
session lasting, on average, N classifications per volunteer, and present the
highly skewed distributions of these quantities. We comment on the scalability
of the \sw system to the wide field survey era, and its potential to operate
beyond its design as a supervised classification system.

@@

In this paper, we describe the \sw project, an web-based system  conceived to
address the visual inspection problem in gravitational lens detection for future
large surveys via crowd-sourcing. Implemented as a Zooniverse project, it is
designed to provide a {\it gravitational lens discovery service} to survey teams
looking for lenses in wide field imaging data. In a companion paper (More et al,
in preparation, herafter \PaperTwo) we will present the new gravitational lenses
discovered in our first, experimental, lens search, and begin to investigate the
differences between lens detections made in \sw and those made with automated
techniques. Here though, we simply try to answer the following questions:

@@

\item How reliably can we find gravitational lenses using the \sw
system? What is the completeness of the sample produced likely to be?

@@

Our basic method in this paper is to analyze the performance of the \sw system
on the ``training set'' of simulated lenses and known non-lenses. This allows us
to estimate completeness and purity with respect to gravitational lenses that
have the same properties of the training set. In \PaperTwo, we carry out a
complementary analysis using a sample of ``known'' (reported in the literature)
lenses.

This paper is organised as follows.  In \Sref{sec:design} we introduce the \sw
classification interface and the volunteers who make up the \sw
collaboration,  explain how we use the training images, and describe our
two-stage candidate selection strategy. We then briefly introduce, in
\Sref{sec:data}, the particular dataset used in the first experimental tests
of the \sw system, and how we prepared the images prior to displaying them in
the web interface. In \Sref{sec:swap} we describe our methodology for
interpreting the classifications made by the volunteers, and then present the
results of system performance tests  made on the training images in
\Sref{sec:results}.  We discuss the implications of our results for future
lens searches in \Sref{sec:discuss} and draw conclusions in
\Sref{sec:conclude}.

@@

The basic steps of a visual search for gravitational lenses are: 1) prepare
the images, 2) display them to an inspector, 3) record the inspector's
classification of each image (as, for example, containing a lens candidate or
not) and 4) analyze that classification along with all others to produce a
final candidate list. We describe step 1 in \Sref{sec:data} and step 4 in
\Sref{sec:swap}. In this section we take a volunteer's eye view and begin by
describing the \sw classification interface, the crowd of volunteers, and the
interactions between the two.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}
\centering\includegraphics[width=0.9\linewidth]{sw-system-figs/sw-screengrab-marker+feedback.png}
\caption{Screenshot of the \sw classification interface.}
\label{fig:screenshot}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

A screenshot of the \sw classification interface (CI) is shown in
\Fref{fig:screenshot}. The CI is the centrepiece of the \sw website,
\texttt{http://spacewarps.org}; the web application is written in coffeescript,
css and html and follows the general design of others written by the Zooniverse
team.\footnote{The \sw web application code is open source and can be accessed
from \texttt{https://github.com/zooniverse/Lens-Zoo}}  The focus of the CI is a
large display of a pre-prepared PNG image of the ``subject'' being inspected.
When the image is clicked on by the volunteer, a marker symbol appears where the
pointer was. Several markers can be placed.

@@

Gravitational lenses are unfamiliar objects to volunteers who are new
to the site. New volunteers need to learn what lenses look like as quickly as
possible, so that they can contribute informative classifications. They also
need to learn what lenses do not look like, in order to reduce the false
positive detection rate. There are three primary mechanisms in the \sw system
for teaching the volunteers what to look for. These are, in the order in which
they are encountered, an inline tutorial, instant feedback,
and a ``Spotter's Guide.'' As well as this, we provide ``About'', ``FAQ'' and ``Science'' pages explaining the physics of gravitational lensing. While we expect that the insight from this static material should help volunteers make sense of the features in the images, we focus on the more dynamic, activity-based training early, when engaging new volunteers to participate takes priority.

@@

In Figures~\ref{fig:training-gallery:sims}~and~\ref{fig:training-gallery:duds}
we show example training images from the first \sw project (\Sref{sec:data}
below).

@@

The instant feedback provides real-time educational responses to the
volunteers as they start classifying; as well as this dynamic system, \sw
provides a static reference work for volunteers to consult when in doubt about
how to perform the task. This ``Spotter's Guide'' is a set of webpages showing
example lenses, both real and simulated, and also some common false positives,
drawn from the pool of survey images. The non-lenses were identified by three
of us (AV, AM and PM) while inspecting a small set of survey images in order
to define the ``dud'' training images. For easy reference, the lenses are
divided by type (for example, ``lensed galaxies,'' ``lensed quasars'' and
``cluster lenses''), as are the false positives (for example, ``Rings and
Spirals,'' ``Mergers,'' ``Artifacts'' and so on). The example images are
accompanied by explanatory text. The Spotter's Guide is reached via a button
on the left hand side, or the hyperlinked thumbnail images of the ``Quick
Reference'' provided on the right hand side, of the classification interface.

@@

We refer the reader to \PaperTwo for the details of the particular set of
imaging survey data used in this first \sw project. Here, we summarize very
briefly the choices that were made, in order to provide the context for our
general description and illustrations of the \sw system.

@@

The CFHT Legacy Survey \citep[CFHTLS,][]{CFHTLS} covered 171 square degrees of
approximately equatorial sky, in four patches distributed in right ascension.
With high and homogeneous image quality (the mean seeing in the $g$-band is
0.78''), and reaching limiting magnitudes of around 25 across the $ugriz$ filter
set, this survey has yielded several dozen new gravitational lenses on both
galaxy and group scales
\citep{GavazziEtal2014,SonnenfeldEtal13,CabanacEtal2007,MoreEtal2012}. The
quality of the data, combined with the presence of these comparison ``known
lens'' samples, makes this a natural choice against which to develop and test
the \sw system. The CFHTLS is also well-representative of the data quality
expected from several next-generation sky surveys, such as DES, KiDS, HSC and
LSST.

@@

Having described the classification interface, the training images and the
test images,  we now outline our methodology for interpreting the interactions
of the volunteers with the identification interface, and then describe how we
applied this methodology in the two classification stages in the CFHTLS
project in the \sw Analysis Pipeline (SWAP) code.\footnote{The open source
SWAP code is available from
\texttt{https://github.com/drphilmarshall/SpaceWarps}}

@@

While the \sw web app is live, and classifications are being made, we perform an
online analysis of the classifications,  updating a probabilistic model of every
(anonymous) volunteer's data, and also updating the posterior probability that
each subject (in both the training and test sets) contains a lens, on a daily
basis. This gives us a dynamic estimate of the posterior probability for  any
given  subject being a lens, given all classifications of it to date. Assigning
thresholds in this lens probability then allows us to make good decisions about
whether or not to retire a subject from the system, in order to focus attention
on new images.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}
\centering\includegraphics[width=0.9\linewidth]{sw-system-figs/CFHTLS_2013-10-29_10:16:35_probabilities.png}
\caption{Typical \SW Agent confusion matrix elements. At a particular
snapshot, 200 randomly-selected agents are shown distributed over the unit plane, with a
tendency to move towards the ``astute'' region in the upper right hand
quadrant as each agent's volunteer views more images. Yellow point size is
proprtional to the number of images classified; green point size shows
agent-perceived ``skill.''}
\label{fig:swap:agent-probabilities}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}
\centering\includegraphics[width=0.9\linewidth]{sw-system-figs/CFHTLS_2013-10-29_10:16:35_histories.png}
\caption{Typical \SW Agent histories. The ``skill'' of the  same 200 random
agents  as in \Fref{fig:swap:agent-probabilities} is plotted in green as a function
of the number  of subjects classified (``effort''). The yellow histogram in
the background shows the distribution of effort.}
\label{fig:swap:agent-histories}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

In this section we present our findings about the performance of the  \sw
system, in terms of the information  contributed by the crowd in
\Sref{sec:results:crowd}, and the overall classifications of the training set
that they made.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}
\centering\includegraphics[width=0.9\linewidth]{sw-system-figs/all_skill_contribution_experience_education.png}
\caption{Key properties and contributions of the \sw crowd. Plotted are the
1-D and 2-D marginalized distributions for the logarithms of the
properties of the agents described in the text. The \StageOne agents are shown
in blue, the \StageTwo agents in orange.}
\label{fig:crowd:cornerplot}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\Fref{fig:crowd:cornerplot} shows the \sw crowd to have quite broad
distributions of logarithmic effort, skill, and contribution. To better
quantify the contributions made by the volunteers, we show their cumulative
distribution on a linear scale in \Fref{fig:crowd:cumulplot}. This plot shows
clearly the importance of the hardest-working, most active volunteers: at
\StageOne,  1.0\% of the volunteers -- 375 people -- made 90\% of the
contribution.  At \StageTwo, where it was not possible to make as
many classifications before running out of subjects, 7.2\% of the volunteers
-- 141 people -- made 90\% of the contribution.

However, it is not the case that only these small groups were capable of
making this large contribution.
% : 9118 volunteers were ``experienced'' in that
% they had all classified at least 10 training images; the 375 highest
% contributing volunteers make up just 4\% of this experienced volunteer pool.
The cumulative distribution of agent skill is shown in
\Fref{fig:crowd:cumulskillplot}: these distributions are significantly broader
than the corresponding distributions of agent contribution in
\Fref{fig:crowd:cumulplot}. The most skilled 20\% of agents possess only  79\%
of the skill at \StageOne, and 77\% at \StageTwo. The inexperienced volunteers
also possess a significant fraction of the skill: the most skillful 20\% of
experienced volunteers (1824 people)  possess just 43\% of the total skill.
The level of contribution made at \sw by experienced volunteers is largely a
matter of choice (or perhaps, availability of time!).

@@

How fast does the \sw crowd classify subjects? Each agent records the timestamp
of each classification its volunteer makes; by measuring the time lags between
successive classifications we can make estimates of the crowd's classification
and contribution speed. We plot these two quantities for both \StageOne and \StageTwo in \Fref{fig:results:speed}, normalizing the speed and time axes to the
respective totals. The fractional classification rates in each stage of the survey fall off in approximately the same way, despite the factor of nearly 20 difference in crowd size. \StageOne (consisting of $\sim430,000$ subjects) was completed in around 5000 hours (by some 37,000 participants), with classification rates in the first few days averaging at $\sim10^4$ per hour, stimulated by various forms of advertising (press releases, and emails to registered Zooniverse users). The asymptotic classification rate was $\sim10^3$ per hour. The average skill was found to be approximately constant over the lifetime of \StageOne, leading to a contribution rate that tracks closely the classification rate. (A 10\% increase in average skill was seen over the first 40 days, and a decrease of the same amount in the last 40 days -- not enough to cause a significant difference between classification and contribution rate behavior, but perhaps reflecting a learning period at the start and a decrease in participation late on.) \StageTwo (3700 subjects) was completed in around 600 hours by around 2000 participants, with classification rates starting at $~\sim2000$ per hour and decaying to $\sim100$ per hour.

@@

We now quantify the performance of the \sw system in terms of the recovery of
the training set images. At \StageOne, this set contains around 5712 simulated
lenses, and 450 duds; at \StageTwo, we used 152 simulated lenses and 201 duds.
\Fref{fig:results:sample:roc} shows receiver operating characteristic (ROC)
curves for CFHTLS \StageOne and \StageTwo. These plots show the true positive
rate (TPR), the number of sims correctly detected divided by the total number of
sims in the training set, and the false positive rate (FPR), the number of duds
incorrectly detected  divided by total number of duds in the training set, both
for a given sample of detections defined by a particular probability threshold,
which varies along the curves.  In both stages, these curves show that true
positive rates of  around 90\% were achieved, at very low false positive rates.
For comparison we show the results of an analysis where the classifications of
training images were ignored, and none of the agents allowed to learn: they were
instead assigned initial values of their confusion matrices of 0.75 for each
element, which then remained constant. This emulates a very simple unweighted
voting scheme, where all classifications are treated equally. In this case, the
TPR remains under 80\% in \StageOne and 60\% in \StageTwo, thus quantifying  the
benefit of including training images and allowing the agents to learn. The
choice of initial confusion matrix is not very important: the same 0.75 initial
values applied to normal, learning agents results in a slightly lower TPR than
the default case, indicating that initializing the system less conservatively
results in slightly worse performance.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}
\begin{minipage}{0.45\linewidth}
  \centering\includegraphics[width=\linewidth]{sw-system-figs/stage1_ROC.png}
\end{minipage}\hfill
\begin{minipage}{0.45\linewidth}
  \centering\includegraphics[width=\linewidth]{sw-system-figs/stage2_ROC.png}
\end{minipage}
\caption{Receiver operating characteristic curves for the \sw system, using
the CFHTLS training set. Left: \StageOne, right: \StageTwo.}
\label{fig:results:sample:roc}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}
\centering\includegraphics[width=\linewidth]{sw-system-figs/completeness_purity.png}
\caption{Completeness-estimated purity curves for the \sw system, using
the CFHTLS training set.}
\label{fig:results:sample:CP}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

What can we learn from the results of the previous section, for future
projects? Potential improvements to the \sw system can be divided into three
categories, performance, efficiency and capacity.

@@

\begin{minipage}{\linewidth}
  \begin{minipage}[t]{0.47\linewidth}
    \begin{minipage}{0.46\linewidth}
      \centering\includegraphics[width=\linewidth]{sw-system-figs/ASW0000fgj_gri.png}
    \end{minipage}\hfill
    \begin{minipage}{0.50\linewidth}
      \centering\includegraphics[width=\linewidth]{sw-system-figs/ASW0000fgj_stage1_trajectory.png}
    \end{minipage}
  \end{minipage}\hfill
  \begin{minipage}[t]{0.47\linewidth}
    \begin{minipage}{0.46\linewidth}
      \centering\includegraphics[width=\linewidth]{sw-system-figs/ASW0003j2s_gri.png}
    \end{minipage}\hfill
    \begin{minipage}{0.50\linewidth}
      \centering\includegraphics[width=\linewidth]{sw-system-figs/ASW0003j2s_stage1_trajectory.png}
    \end{minipage}
  \end{minipage}
\end{minipage}
\caption{Illustrative examples of
false negatives (blue) and false positives (red) from the classification of
the \sw CFHTLS training set. The trajectory plot for each of the 4 subjects is
shown to the right of its image. Lefthand panels show the most common types of
trajectories: short step random walks resulting from no high skill classifiers
viewing the subject. The righthand panels show examples where higher skill
classifiers have been involved, causing random walks with longer step lengths
(top) and catastrophic mis-classifications (bottom right). Insets for the false
negatives show the lens feature. The inset for the lower righthand panel shows
where most users believed a lens was located. There is no corresponding inset
for the lower left panel because no particular feature stood out to users.
Instead, users clicked many different features.}
\label{fig:discuss:performance:trajectories}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

% Questions we set ourselves in the introduction:
% \begin{itemize}
% \item How reliably can we find gravitational lenses using the \sw
% system? What is the completeness of the sample produced likely to be?
% \item How noisy is the system? What is the purity of the sample
% produced?
% \item How quickly can lenses be detected, and non-lenses be rejected?
% How many classifications, and so how many volunteers are needed per target?
% \item What can we learn about the scalability of the crowd-sourcing approach?
% \end{itemize}

>>>>

\title[\SW]
{\SW: Crowd-sourcing the Discovery of Gravitational Lenses}

@@

We describe \SW, a novel gravitaional lens discovery service that
yields samples of high purity and completeness through crowd-sourced
visual inspection.
Carefully
produced color composite images are displayed to volunteers via a
classification interface which records their estimates of the positions of
candidate lensed features. Simulated lenses, and expert-classified non-lenses,
are inserted into the image stream at random intervals; this training set is
used to give the volunteers feedback on their performance, and to estimate a
dynamically-updated probability for any given image to contain a lens. Low
probability systems are retired from the site periodically, concentrating the
sample towards a set of candidates; this ``\StageOne'' set is then re-classified
by the volunteers in a second  refinement stage. Analyzing the classification
of the training set, we predict that the first stage alone should yield a
sample that is C\% complete, while leading to the rejection of R\% of the
initial target sample. Having divided the 150 square degree CFHTLS imaging
survey into 430000 overlapping 70 by 70 arcminute tiles and displayed them on
the site, we were joined by 33000 volunteers who contributed X million image
classifications over the course of N months. The sample was reduced to 3500
\StageOne candidates; these were then refined to yield a sample of 1400
candidates rankable by their \StageTwo probability. We expect this sample to be
X\% complete and Y\% pure at a threshold of 95\% classification probability.
We find that, on average, and given the assumptions we make in our analysis,
we need 9 classifications per image during the first stage, X in the second.
We estimate the mean information contributed per person to be X bits, over a
session lasting, on average, N classifications per volunteer, and present the
highly skewed distributions of these quantities. We comment on the scalability
of the \SW system to the wide field survey era, and its potential to operate
beyond its design as a supervised classification system.

@@

In this paper, we describe the \SW project, an web-based system  conceived to
address the visual inspection problem in gravitational lens detection for future
large surveys via crowd-sourcing. Implemented as a Zooniverse project, it is
designed to provide a {\it gravitational lens discovery service} to survey teams
looking for lenses in wide field imaging data. In a companion paper (More et al,
in preparation, herafter \PaperTwo) we will present the new gravitational lenses
discovered in our first, experimental, lens search, and begin to investigate the
differences between lens detections made in \SW and those made with automated
techniques. Here though, we simply try to answer the following questions:

@@

\item How reliably can we find gravitational lenses using the \SW
system? What is the completeness of the sample produced likely to be?

@@

Our basic method in this paper is to analyze the performance of the \SW system
on the ``training set'' of simulated lenses and known non-lenses. This allows us
to estimate completeness and purity with respect to gravitational lenses that
have the same properties of the training set. In \PaperTwo, we carry out a
complementary analysis using a sample of ``known'' (reported in the literature)
lenses.

This paper is organised as follows.  In \Sref{sec:design} we introduce the \SW
classification interface and the volunteers who make up the \SW
collaboration,  explain how we use the training images, and describe our
two-stage candidate selection strategy. We then briefly introduce, in
\Sref{sec:data}, the particular dataset used in the first experimental tests
of the \SW system, and how we prepared the images prior to displaying them in
the web interface. In \Sref{sec:swap} we describe our methodology for
interpreting the classifications made by the volunteers, and then present the
results of system performance tests  made on the training images in
\Sref{sec:results}.  We discuss the implications of our results for future
lens searches in \Sref{sec:discuss} and draw conclusions in
\Sref{sec:conclude}.

@@

The basic steps of a visual search for gravitational lenses are: 1) prepare
the images, 2) display them to an inspector, 3) record the inspector's
classification of each image (as, for example, containing a lens candidate or
not) and 4) analyze that classification along with all others to produce a
final candidate list. We describe step 1 in \Sref{sec:data} and step 4 in
\Sref{sec:swap}. In this section we take a volunteer's eye view and begin by
describing the \SW classification interface, the crowd of volunteers, and the
interactions between the two.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}
\centering\includegraphics[width=0.9\linewidth]{sw-system-figs/sw-screengrab-marker+feedback.png}
\caption{Screenshot of the \SW classification interface.}
\label{fig:screenshot}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

A screenshot of the \SW classification interface (CI) is shown in
\Fref{fig:screenshot}. The CI is the centrepiece of the \SW website,
\texttt{http://spacewarps.org}; the web application is written in coffeescript,
css and html and follows the general design of others written by the Zooniverse
team.\footnote{The \SW web application code is open source and can be accessed
from \texttt{https://github.com/zooniverse/Lens-Zoo}}  The focus of the CI is a
large display of a pre-prepared PNG image of the ``subject'' being inspected.
When the image is clicked on by the volunteer, a marker symbol appears where the
pointer was. Several markers can be placed.

@@

Gravitational lenses are unfamiliar objects to volunteers who are new
to the site. New volunteers need to learn what lenses look like as quickly as
possible, so that they can contribute informative classifications. They also
need to learn what lenses do not look like, in order to reduce the false
positive detection rate. There are three primary mechanisms in the \SW system
for teaching the volunteers what to look for. These are, in the order in which
they are encountered, an inline tutorial, instant feedback,
and a ``Spotter's Guide.'' As well as this, we provide ``About'', ``FAQ'' and ``Science'' pages explaining the physics of gravitational lensing. While we expect that the insight from this static material should help volunteers make sense of the features in the images, we focus on the more dynamic, activity-based training early, when engaging new volunteers to participate takes priority.

@@

In Figures~\ref{fig:training-gallery:sims}~and~\ref{fig:training-gallery:duds}
we show example training images from the first \SW project (\Sref{sec:data}
below).

@@

The instant feedback provides real-time educational responses to the
volunteers as they start classifying; as well as this dynamic system, \SW
provides a static reference work for volunteers to consult when in doubt about
how to perform the task. This ``Spotter's Guide'' is a set of webpages showing
example lenses, both real and simulated, and also some common false positives,
drawn from the pool of survey images. The non-lenses were identified by three
of us (AV, AM and PM) while inspecting a small set of survey images in order
to define the ``dud'' training images. For easy reference, the lenses are
divided by type (for example, ``lensed galaxies,'' ``lensed quasars'' and
``cluster lenses''), as are the false positives (for example, ``Rings and
Spirals,'' ``Mergers,'' ``Artifacts'' and so on). The example images are
accompanied by explanatory text. The Spotter's Guide is reached via a button
on the left hand side, or the hyperlinked thumbnail images of the ``Quick
Reference'' provided on the right hand side, of the classification interface.

@@

We refer the reader to \PaperTwo for the details of the particular set of
imaging survey data used in this first \SW project. Here, we summarize very
briefly the choices that were made, in order to provide the context for our
general description and illustrations of the \SW system.

@@

The CFHT Legacy Survey \citep[CFHTLS,][]{CFHTLS} covered 171 square degrees of
approximately equatorial sky, in four patches distributed in right ascension.
With high and homogeneous image quality (the mean seeing in the $g$-band is
0.78''), and reaching limiting magnitudes of around 25 across the $ugriz$ filter
set, this survey has yielded several dozen new gravitational lenses on both
galaxy and group scales
\citep{GavazziEtal2014,SonnenfeldEtal13,CabanacEtal2007,MoreEtal2012}. The
quality of the data, combined with the presence of these comparison ``known
lens'' samples, makes this a natural choice against which to develop and test
the \SW system. The CFHTLS is also well-representative of the data quality
expected from several next-generation sky surveys, such as DES, KiDS, HSC and
LSST.

@@

Having described the classification interface, the training images and the
test images,  we now outline our methodology for interpreting the interactions
of the volunteers with the identification interface, and then describe how we
applied this methodology in the two classification stages in the CFHTLS
project in the \SW Analysis Pipeline (SWAP) code.\footnote{The open source
SWAP code is available from
\texttt{https://github.com/drphilmarshall/SpaceWarps}}

@@

While the \SW web app is live, and classifications are being made, we perform an
online analysis of the classifications,  updating a probabilistic model of every
(anonymous) volunteer's data, and also updating the posterior probability that
each subject (in both the training and test sets) contains a lens, on a daily
basis. This gives us a dynamic estimate of the posterior probability for  any
given  subject being a lens, given all classifications of it to date. Assigning
thresholds in this lens probability then allows us to make good decisions about
whether or not to retire a subject from the system, in order to focus attention
on new images.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}
\centering\includegraphics[width=0.9\linewidth]{sw-system-figs/CFHTLS_2013-10-29_10:16:35_probabilities.png}
\caption{Typical \SW agent confusion matrix elements. At a particular
snapshot, 200 randomly-selected agents are shown distributed over the unit plane, with a
tendency to move towards the ``astute'' region in the upper right hand
quadrant as each agent's volunteer views more images. Yellow point size is
proprtional to the number of images classified; green point size shows
agent-perceived ``skill.''}
\label{fig:swap:agent-probabilities}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}
\centering\includegraphics[width=0.9\linewidth]{sw-system-figs/CFHTLS_2013-10-29_10:16:35_histories.png}
\caption{Typical \SW agent histories. The ``skill'' of the  same 200 random
agents  as in \Fref{fig:swap:agent-probabilities} is plotted in green as a function
of the number  of subjects classified (``effort''). The yellow histogram in
the background shows the distribution of effort.}
\label{fig:swap:agent-histories}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

In this section we present our findings about the performance of the \SW
system, in terms of the information  contributed by the crowd in
\Sref{sec:results:crowd}, and the overall classifications of the training set
that they made.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}
\centering\includegraphics[width=0.9\linewidth]{sw-system-figs/all_skill_contribution_experience_education.png}
\caption{Key properties and contributions of the \SW crowd. Plotted are the
1-D and 2-D marginalized distributions for the logarithms of the
properties of the agents described in the text. The \StageOne agents are shown
in blue, the \StageTwo agents in orange.}
\label{fig:crowd:cornerplot}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\Fref{fig:crowd:cornerplot} shows the \SW crowd to have quite broad
distributions of logarithmic effort, skill, and contribution. To better
quantify the contributions made by the volunteers, we show their cumulative
distribution on a linear scale in \Fref{fig:crowd:cumulplot}. This plot shows
clearly the importance of the hardest-working, most active volunteers: at
\StageOne,  1.0\% of the volunteers -- 375 people -- made 90\% of the
contribution.  At \StageTwo, where it was not possible to make as
many classifications before running out of subjects, 7.2\% of the volunteers
-- 141 people -- made 90\% of the contribution.

However, it is not the case that only these small groups were capable of
making this large contribution.
% : 9118 volunteers were ``experienced'' in that
% they had all classified at least 10 training images; the 375 highest
% contributing volunteers make up just 4\% of this experienced volunteer pool.
The cumulative distribution of agent skill is shown in
\Fref{fig:crowd:cumulskillplot}: these distributions are significantly broader
than the corresponding distributions of agent contribution in
\Fref{fig:crowd:cumulplot}. The most skilled 20\% of agents possess only  79\%
of the skill at \StageOne, and 77\% at \StageTwo. The inexperienced volunteers
also possess a significant fraction of the skill: the most skillful 20\% of
experienced volunteers (1824 people)  possess just 43\% of the total skill.
The level of contribution made at \SW by experienced volunteers is largely a
matter of choice (or perhaps, availability of time!).

@@

How fast does the \SW crowd classify subjects? Each agent records the timestamp
of each classification its volunteer makes; by measuring the time lags between
successive classifications we can make estimates of the crowd's classification
and contribution speed. We plot these two quantities for both \StageOne and \StageTwo in \Fref{fig:results:speed}, normalizing the speed and time axes to the
respective totals. The fractional classification rates in each stage of the survey fall off in approximately the same way, despite the factor of nearly 20 difference in crowd size. \StageOne (consisting of $\sim430,000$ subjects) was completed in around 5000 hours (by some 37,000 participants), with classification rates in the first few days averaging at $\sim10^4$ per hour, stimulated by various forms of advertising (press releases, and emails to registered Zooniverse users). The asymptotic classification rate was $\sim10^3$ per hour. The average skill was found to be approximately constant over the lifetime of \StageOne, leading to a contribution rate that tracks closely the classification rate. (A 10\% increase in average skill was seen over the first 40 days, and a decrease of the same amount in the last 40 days -- not enough to cause a significant difference between classification and contribution rate behavior, but perhaps reflecting a learning period at the start and a decrease in participation late on.) \StageTwo (3700 subjects) was completed in around 600 hours by around 2000 participants, with classification rates starting at $~\sim2000$ per hour and decaying to $\sim100$ per hour.

@@

We now quantify the performance of the \SW system in terms of the recovery of
the training set images. At \StageOne, this set contains around 5712 simulated
lenses, and 450 duds; at \StageTwo, we used 152 simulated lenses and 201 duds.
\Fref{fig:results:sample:roc} shows receiver operating characteristic (ROC)
curves for CFHTLS \StageOne and \StageTwo. These plots show the true positive
rate (TPR), the number of sims correctly detected divided by the total number of
sims in the training set, and the false positive rate (FPR), the number of duds
incorrectly detected  divided by total number of duds in the training set, both
for a given sample of detections defined by a particular probability threshold,
which varies along the curves.  In both stages, these curves show that true
positive rates of  around 90\% were achieved, at very low false positive rates.
For comparison we show the results of an analysis where the classifications of
training images were ignored, and none of the agents allowed to learn: they were
instead assigned initial values of their confusion matrices of 0.75 for each
element, which then remained constant. This emulates a very simple unweighted
voting scheme, where all classifications are treated equally. In this case, the
TPR remains under 80\% in \StageOne and 60\% in \StageTwo, thus quantifying  the
benefit of including training images and allowing the agents to learn. The
choice of initial confusion matrix is not very important: the same 0.75 initial
values applied to normal, learning agents results in a slightly lower TPR than
the default case, indicating that initializing the system less conservatively
results in slightly worse performance.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}
\begin{minipage}{0.45\linewidth}
  \centering\includegraphics[width=\linewidth]{sw-system-figs/stage1_ROC.png}
\end{minipage}\hfill
\begin{minipage}{0.45\linewidth}
  \centering\includegraphics[width=\linewidth]{sw-system-figs/stage2_ROC.png}
\end{minipage}
\caption{Receiver operating characteristic curves for the \SW system, using
the CFHTLS training set. Left: \StageOne, right: \StageTwo.}
\label{fig:results:sample:roc}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}
\centering\includegraphics[width=\linewidth]{sw-system-figs/completeness_purity.png}
\caption{Completeness-estimated purity curves for the \SW system, using
the CFHTLS training set.}
\label{fig:results:sample:CP}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

What can we learn from the results of the previous section, for future
projects? Potential improvements to the \SW system can be divided into three
categories, performance, efficiency and capacity.

@@

\begin{minipage}{\linewidth}
  \begin{minipage}[t]{0.47\linewidth}
    \begin{minipage}{0.46\linewidth}
      \centering\includegraphics[width=\linewidth]{sw-system-figs/ASW0000fgj_gri.png}
    \end{minipage}\hfill
    \begin{minipage}{0.50\linewidth}
      \centering\includegraphics[width=\linewidth]{sw-system-figs/ASW0000fgj_stage1_trajectory.png}
    \end{minipage}
  \end{minipage}\hfill
  \begin{minipage}[t]{0.47\linewidth}
    \begin{minipage}{0.46\linewidth}
      \centering\includegraphics[width=\linewidth]{sw-system-figs/ASW0003j2s_gri.png}
    \end{minipage}\hfill
    \begin{minipage}{0.50\linewidth}
      \centering\includegraphics[width=\linewidth]{sw-system-figs/ASW0003j2s_stage1_trajectory.png}
    \end{minipage}
  \end{minipage}
\end{minipage}
\caption{Illustrative examples of
false negatives (blue) and false positives (red) from the classification of
the \SW CFHTLS training set. The trajectory plot for each of the 4 subjects is
shown to the right of its image. Lefthand panels show the most common types of
trajectories: short step random walks resulting from no high skill classifiers
viewing the subject. The righthand panels show examples where higher skill
classifiers have been involved, causing random walks with longer step lengths
(top) and catastrophic mis-classifications (bottom right). Insets for the false
negatives show the lens feature. The inset for the lower righthand panel shows
where most users believed a lens was located. There is no corresponding inset
for the lower left panel because no particular feature stood out to users.
Instead, users clicked many different features.}
\label{fig:discuss:performance:trajectories}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

% Questions we set ourselves in the introduction:
% \begin{itemize}
% \item How reliably can we find gravitational lenses using the \SW
% system? What is the completeness of the sample produced likely to be?
% \item How noisy is the system? What is the purity of the sample
% produced?
% \item How quickly can lenses be detected, and non-lenses be rejected?
% How many classifications, and so how many volunteers are needed per target?
% \item What can we learn about the scalability of the crowd-sourcing approach?
% \end{itemize}
